Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-22 bbbq_article.tex
Process feedback Geert

% GvdB: A narrative was missing a bit. Why was this done? 
To confirm that peptides stemming from TMHs were presented in MHC-I and MHC-II,
we reanalyzed published peptide elution studies.
Table \ref{tab:elution} shows the percentage of epitopes derived 
from a TMH
found in MHC-I and MHC-II elution studies \richel{refs}, 
for the two topology prediction tools TMHMM and PureseqTM \richel{refs}. 
Regardless of the prediction, 
at least 100 epitopes were predicted to be derived from a TMH. 
% GvdB: Also add a conclusion at the end of the paragraph.
From these findings, we conclude that PureseqTM and TMHMM 
result in prediction of a similar number of TMHs 
and that peptides derived from TMHs have been identified for both MHC-I and -II.

@@

We recently showed that peptides derived from TMHs of human proteins 
were predicted to be over-presented in MHC-I. 
Here, we wondered if this finding would be general 
and if peptides stemming from TMHs of microbial pathogens 
would also be over-presented.
Figure \ref{fig:1} shows the percentages of MHC-I epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc1}) 
for the exact TMH and epitope counts.
\richel{GvdB: Also provide a short conclusion}

@@

\richel{GvdB: Again a rationale}
Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc2}) 
for the TMH and epitope counts.
\richel{GvdB: And a conclusion}

>>>>

% GvdB: A narrative was missing a bit. Why was this done? 
To confirm that peptides stemming from TMHs were presented in MHC-I and MHC-II,
we reanalyzed published peptide elution studies.
Table \ref{tab:elution} shows the percentage of epitopes derived 
from a TMH
found in MHC-I and MHC-II elution 
studies (\cite{schellens2015comprehensive} and \cite{bergseng2015different} respectively), 
for the two topology prediction tools TMHMM and 
PureseqTM (\cite{krogh2001predicting} and \cite{wang2019efficient} respectively). 
Regardless of the prediction, 
at least 100 epitopes were predicted to be derived from a TMH. 
% GvdB: Also add a conclusion at the end of the paragraph.
From these findings, we conclude that PureseqTM and TMHMM 
result in prediction of a similar number of TMHs 
and that peptides derived from TMHs have been identified for both MHC-I and -II.

@@

We recently showed that peptides derived from TMHs of human proteins 
were predicted to be over-presented in MHC-I. 
Here, we wondered if this finding would be general 
and if peptides stemming from TMHs of microbial pathogens 
would also be over-presented.
Figure \ref{fig:1} shows the percentages of MHC-I epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc1}) 
for the exact TMH and epitope counts.
We found that also for pathogen epitopes derived from TMHs are
over-presented. 
The extent of the over-presentation is similar between the haplotypes:
if a haplotype if prone to present TMH-derived epitopes from
human proteins, it is also prone to present such epitopes of
bacterial and viral proteins.

@@

Where TMH-derived epitopes are over-presented by MHC-I,
we wondered if this finding would also generalize to MHC-II.
Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc2}) 
for the TMH and epitope counts.
We show that MHC-II has the same pattern of over-presentation
as MHC-I, yet this over-presentation is more extreme.
Also for MHC-II, we observe that the extent the which TMH-derived
epitopes are presented is similar between the haplotypes, regardless
of the protein source.
